LIONFISH: an expLoratory Interactive tOol for dyNamic visualization and identiFicatIon multidimenSional mecHanisms

### 2024-09-27 manuscript.tex
more quotes to proper double quotes

The Austrian Vacation Activities dataset comprises responses from 2,961 adult tourists who spent their holiday in Austria during the 1997/98 season. Participants were asked to evaluate the importance of 27 different activities during their vacation. The survey categorized responses based on four levels of importance: ``totally important'', ``mostly important'', ``a bit important'', and ``not important". For analysis, the responses were binarized: a value of 1 was assigned if the activity was rated as ``totally important'', and a value of 0 if any of the other categories were selected. The survey was conducted by the Europäisches Tourismus Institut GmbH at the University of Trier and focused exclusively on tourists who did not stay in the country's capital cities.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_pre.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Austrian vacation activities dataset, with manually adjusted projections. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. Changing the projection axes of ``going to a spa'', ``museums'', ``sightseeing" and ``using health facilities" reveals the preferences and overlap of clusters 1 and 3.}
    \label{fig:winter_cl7_pre}
\end{figure}

@@

Since we are particularly interested in tourists who did not spend time with friends, we can extend the projection axis ``Friends" outward to separate the data based on that feature. Datapoints in the opposite direction of the ``Friends" axes are the solo travellers we are interested in, which can be seen in Figure \ref{fig:aus_preselection} on the left side of the top left plot. Subsequently, we can pull all other projection axes in one direction to separate data points based on their overall activity level. Tourists that fall in the direction of the axes generally engaged in more activities compared to those in the opposite direction of the projection axes. This separation is evident, as observations in subset 6 (brown) are located opposite the axes, and the heatmap shows that they did not engage in many activities. Similarly we can also see that subset 2 (orange), which contains quite active tourists, is shifted towards the direction of the axes.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{aus_preselection.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Australian vacation activities dataset, with the projection axes of the feature ``Friends" pointing into one direction and all the other ones into another one. Top left: 2D tour. Top right: 1D tour. Bottom left: Mosaic plot. Bottom right: Heatmap with the intra cluster fraction. We can see how the feature ``Friends" and the general activity level (represented by the other projection axes pointing into one direction) separates the data.}
    \label{fig:aus_preselection}
\end{figure}

>>>>

The Austrian Vacation Activities dataset comprises responses from 2,961 adult tourists who spent their holiday in Austria during the 1997/98 season. Participants were asked to evaluate the importance of 27 different activities during their vacation. The survey categorized responses based on four levels of importance: ``totally important'', ``mostly important'', ``a bit important'', and ``not important''. For analysis, the responses were binarized: a value of 1 was assigned if the activity was rated as ``totally important'', and a value of 0 if any of the other categories were selected. The survey was conducted by the Europäisches Tourismus Institut GmbH at the University of Trier and focused exclusively on tourists who did not stay in the country's capital cities.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_pre.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Austrian vacation activities dataset, with manually adjusted projections. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. Changing the projection axes of ``going to a spa'', ``museums'', ``sightseeing'' and ``using health facilities'' reveals the preferences and overlap of clusters 1 and 3.}
    \label{fig:winter_cl7_pre}
\end{figure}

@@

Since we are particularly interested in tourists who did not spend time with friends, we can extend the projection axis ``Friends'' outward to separate the data based on that feature. Datapoints in the opposite direction of the ``Friends'' axes are the solo travellers we are interested in, which can be seen in Figure \ref{fig:aus_preselection} on the left side of the top left plot. Subsequently, we can pull all other projection axes in one direction to separate data points based on their overall activity level. Tourists that fall in the direction of the axes generally engaged in more activities compared to those in the opposite direction of the projection axes. This separation is evident, as observations in subset 6 (brown) are located opposite the axes, and the heatmap shows that they did not engage in many activities. Similarly we can also see that subset 2 (orange), which contains quite active tourists, is shifted towards the direction of the axes.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{aus_preselection.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Australian vacation activities dataset, with the projection axes of the feature ``Friends'' pointing into one direction and all the other ones into another one. Top left: 2D tour. Top right: 1D tour. Bottom left: Mosaic plot. Bottom right: Heatmap with the intra cluster fraction. We can see how the feature ``Friends'' and the general activity level (represented by the other projection axes pointing into one direction) separates the data.}
    \label{fig:aus_preselection}
\end{figure}
